A re-examination of the role of friction in the original Social Force Model

### 2019-05-21 paper.tex
avance hasta correccion 6 del referee 2

Researchers turned back to examine the available data on the velocity and flux 
behavior for different density environments \cite{helbing3,seyfried,seyfried1}. 
Ref.~\cite{helbing3} \textcolor{red}{summarizes} empirical data from 
literature, and their own data set, acquired from videos of the Muslim 
pilgrimage in Mina-Makkah (2006). They showed from the empirical fundamental 
diagram (flux $J$ versus density $\rho$) that highly dense crowds (seemingly up 
to $10\,$p/m$^2$) do not drive the pedestrians velocity to zero, although the 
reasons for this remain rather obscure.   \\

@@

\begin{equation}
        \mathbf{f}_d^ {(i)}(t) =  
m_i\,\displaystyle\frac{v_d^{(i)}\,\mathbf{e}_d^
{(i)}(t)-\mathbf{v}^{(i)}(t)}{\tau} \label{desired}
\end{equation}

@@

\begin{equation}
        \mathbf{f}_s^{(ij)} = A_i\,e^{(R_{ij}-r_{ij})/B_i}\mathbf{n}_{ij} 
        \label{social}
\end{equation}

@@

\begin{equation}
        \mathbf{f}_g^{(ij)} = 
\kappa\,(R_{ij}-r_{ij})\,\Theta(R_{ij}-r_{ij})\,\Delta
\mathbf{v}^{(ij)}\cdot\mathbf{t}_{ij} 
        \label{granular}
\end{equation}

@@

\begin{equation}
m_i\,\displaystyle\frac{d\mathbf{v}^{(i)}}{dt}=\mathbf{f}_d^{(i)}
+\displaystyle\sum_{j=1}^{N}\displaystyle\mathbf{f}_s^{(ij)}
+\displaystyle\sum_ {
j=1}^{N}\mathbf{f}_g^{(ij)}\label{eq_mov}
\end{equation}

@@

\begin{equation}
\rho(\vec{r},t)=\sum_{j}f(\vec{r}_j(t)-\vec{r}) \label{ec-density}
\end{equation}

@@

\begin{equation}
f(\vec{r}_j-\vec{r})=\frac{1}{\pi R^2}\exp[-\left \| \vec{r}_j-\vec{r} \right \|^2/R^2] \label{ec-f}
\end{equation}

@@

\begin{equation}
C_g:P_i~\epsilon~ C_g \Leftrightarrow \exists~ j~\epsilon~C_g / r_{ij} < (R_i+R_j) \label{ec-cluster}
\end{equation}

@@

\subsection{\label{Hypotheses} Hypotheses}

@@

\begin{equation}
 \left\{\begin{array}{lll}
         \mathbf{f}_d' & = & \hat{\mathbf{e}}_d-\mathbf{v}' \\
         && \\
         \mathbf{f}_s' & =& \mathcal{A}\,\exp(r'-d')\,\hat{\mathbf{n}} \\
         && \\
         \mathbf{f}_g' & = & 
\mathcal{K}\,(2r'-d')\,\Theta(2r'-d')\,(\Delta\mathbf{v}'\cdot\hat{\mathbf{t}})\
, 
\hat{\mathbf{t}} \\
        \end{array}\right.\label{eqn_appendix_2}
\end{equation}

@@

\begin{equation}
\displaystyle\frac{dv'}{dt'}(y')=1-v'(y')+f_g'(y'+\delta 
y')-f_g'(y'-\delta y')\label{eqn_appendix_2:1}
 \end{equation}

>>>>

Researchers turned back to examine the available data on the velocity and flux 
behavior for different density environments \cite{Boltes,helbing3,seyfried,seyfried1}. 
Ref.~\cite{helbing3} \textcolor{red}{summarizes} empirical data from 
literature, and their own data set, acquired from videos of the Muslim 
pilgrimage in Mina-Makkah (2006). They showed from the empirical fundamental 
diagram (flux $J$ versus density $\rho$) that highly dense crowds (seemingly up 
to $10\,$p/m$^2$) do not drive the pedestrians velocity to zero, although the 
reasons for this remain rather obscure.   \\

@@

\begin{equation}
        \mathbf{f}_d^ {(i)}(t) =  
m_i\,\displaystyle\frac{v_d^{(i)}\,\mathbf{e}_d^
{(i)}(t)-\mathbf{v}^{(i)}(t)}{\tau}, \label{desired}
\end{equation}

@@

\begin{equation}
        \mathbf{f}_s^{(ij)} = A_i\,e^{(R_{ij}-r_{ij})/B_i}\mathbf{n}_{ij}, 
        \label{social}
\end{equation}

@@

\begin{equation}
        \mathbf{f}_g^{(ij)} = 
\kappa\,(R_{ij}-r_{ij})\,\Theta(R_{ij}-r_{ij})\,\Delta
\mathbf{v}^{(ij)}\cdot\mathbf{t}_{ij}, 
        \label{granular}
\end{equation}

@@

\begin{equation}
m_i\,\displaystyle\frac{d\mathbf{v}^{(i)}}{dt}=\mathbf{f}_d^{(i)}
+\displaystyle\sum_{j=1}^{N}\displaystyle\mathbf{f}_s^{(ij)}
+\displaystyle\sum_ {
j=1}^{N}\mathbf{f}_g^{(ij)},\label{eq_mov}
\end{equation}

@@

\begin{equation}
\rho(\vec{r},t)=\sum_{j}f(\vec{r}_j(t)-\vec{r}), \label{ec-density}
\end{equation}

@@

\begin{equation}
f(\vec{r}_j-\vec{r})=\frac{1}{\pi R^2}\exp[-\left \| \vec{r}_j-\vec{r} \right \|^2/R^2]. \label{ec-f}
\end{equation}

@@

\begin{equation}
C_g:P_i~\epsilon~ C_g \Leftrightarrow \exists~ j~\epsilon~C_g / r_{ij} < (R_i+R_j), \label{ec-cluster}
\end{equation}

@@

\section{\label{Hypotheses} \textcolor{red}{Hypotheses}}

@@

\begin{equation}
 \left\{\begin{array}{lll}
         \mathbf{f}_d' & = & \hat{\mathbf{e}}_d-\mathbf{v}' \\
         && \\
         \mathbf{f}_s' & =& \mathcal{A}\,\exp(r'-d')\,\hat{\mathbf{n}} \\
         && \\
         \mathbf{f}_g' & = & 
\mathcal{K}\,(2r'-d')\,\Theta(2r'-d')\,(\Delta\mathbf{v}'\cdot\hat{\mathbf{t}})\

\hat{\mathbf{t}} \\
        \end{array}\right.\label{eqn_appendix_2}
\end{equation}

@@

\begin{equation}
\displaystyle\frac{dv'}{dt'}(y')=1-v'(y')+f_g'(y'+\delta 
y')-f_g'(y'-\delta y'),\label{eqn_appendix_2:1}
 \end{equation}
